### 2019-03-17 README.Rmd
Use sheild style CI badge [ci skip]

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg?style=svg){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

>>>>

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg?style=sheild){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![codecov](https://codecov.io/gh/ecohealthalliance/citesdb/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
